Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Clean up naive model section

\subsubsection{Linear Interpolation}

@@

Na\"ively, we can simply use linear interpolation to estimate $S$ and
the trapezoidal rule to estimate $Z$.

In this naïve strategy, we perform a hill-climbing search to find a
local maxima. In other words, we rotate in the direction for which
there is a local increase in similarity.

\paragraph{Stopping criterion}

Because we are using hill-climbing, we choose to stop when we hit a
local maxima.

\subsubsection{Parametric Regression}

>>>>

\subsection{Na\"ive model}

@@

As a baseline, we defined a \textit{na\"ive} model which performs a
hill-climbing search over the similarity function until it reaches a
(possibly local) maximum. Once a maximum as been found, the model
computes an estimate of $Z$ by linearly interpolating between sampled
rotations.

When $h_1$ is correct and as the true angle of rotation approaches 0,
the \textit{na\"ive} model should increase in both response and
rotation accuracy, because local maxima will be less likely (and
therefore, it is more likely that the global maxima will be
discovered). For larger angles of rotation, this model should have a
tendency to under-rotate, because it will find local maxima and end
prematurely. Its estimates of $Z$ will usually be overestimates (if it
finds the global maxima, and then terminates) or underestimates (the
rest of the time). This model should almost always be accurate when
$h_0$ is correct.

\subsection{Parametric (Von Mises) model}
